Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
results updated

@@

  \begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
	\caption{Pair distribution functions of aromatic carbons for the
	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
	parallel displaced configurations. Spikes in the distribution mark
	distinct layers. The magnitude of the spikes with respect to the 
	average suggest that the 5 monomer per layer, sandwiched configuration
	possesses the highest degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

  The initial distance between layers can influence the approach towards
  equilibrium.

  Experimental WAXS measurements encode all structural details.

@@

  We varied the relative interlayer orientation between sandwiched and 
  parallel-displaced based on our knowledge of the stability of these two
  pi-stacking modes.

@@

  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns produced from equilibrated MD trajectories shows the most consistency
  with the sandwiched configuration in Basin A.

@@

  The spots that appear in the simulated XRD pattern of the sandwiched
  conformation are a result of the way alkane tails pack together.

@@

  Basin A and Basin B are two configurationally metastable basins.

@@

  The model gives reasonable estimates of ionic conductivity for both phases.

@@

  We applied the crosslinking algorithm to an equilibrated structure in Basin B.

  \begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}

>>>>

    \item However, we do define a pore radius based for our own purposes.
    \item Pore radius was measured by calculating the distance between the center of 
    mass of each aromatic ring and the center of mass of all aromatic rings in their 

@@

  \begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
	\caption{Pair distribution functions of aromatic carbons for the
	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
	parallel displaced configurations. Spikes in the distribution mark
	distinct layers. The magnitude of the spikes with respect to the 
	average suggest that the 5 monomer per layer, sandwiched configuration
	possesses a higher degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

  Experimental WAXS measurements encode all structural details. 
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-pi.
	\item A weak intensity line is located at exactly half the qz value of
	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Equilibrated systems built according to the 3.7 \angstrom 
	layer spacing implied by R-pi are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
	\item We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called Basin B (Figure~\ref{fig:340K_pore}).
	\item It is apparent that this LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Understanding which phase exists experimentally is necessary in order
	to appropriately study the system.
  \end{itemize}

  We varied the relative interlayer orientation between sandwiched and 
  parallel-displaced based on our knowledge of the stability of the two
  pi-stacking modes.
  \begin{itemize}
  	\item We generated simulated X-ray diffraction patterns from the highly
	restrained initial configurations created during equilibration
	\item The patterns establish a difference between the two stacking 
	modes (Figure~\ref{fig:XRDrestrained}).
	\item In each pattern, R-alkanes is present at a distance of $\approx
	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
  	\item R-pi is also present in each pattern, although it appears to 
	intersect R-alkanes because the spacing between aromatic rings is 
	similar to the alkane chain packing.
	\item The difference in aromatic ring spacing between experiment and
	simulation is likely a result of the inability of GAFF to properly handle
	aromatic interactions.
	\item The sandwiched configuration shows R-spots in the expected location.
	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
	\item The parallel displaced configuration contains two lines of high 
	intensity with maximum intensity occurring where they intersect the alkane
	chain region due to constructive interference between the two features.
	\item The lines are located where one would expect to see R-helix and, 
	perhaps coincidentally, the intersection with R-alkanes occurs where one 
	would expect to see R-spots.
	%BJC: might save the following sentence for equilibrium trajectories
	\item As the simulation is progressed, the full line begins to fade 
	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
	where R-helix exists.
  \end{itemize}

@@

  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns produced from equilibrated MD trajectories shows the most consistency
  with the sandwiched configuration in Basin A.
  \begin{itemize}
  	\item Systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom apart in order to guide it towards Basin B.
	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
	\item For ease of reference, the third system will be referred to as the disordered system. %BJC: omit and call it basin B
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.
	\item Equilibration was detected when the distance between pores and the 
	membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
	%BJC: maybe break into a separate paragraph starting here
	\item The equilibrated parallel displaced structure exhibits R-alkanes and
	R-pores in the expected locations. 
	\item Due to low resolution, making out the individual spots of R-pores is
	challenging and can be validated upon full spherical integration of the 3D 
	structure factor. However, the same information can be extracted by measuring 
	the pore spacing as described earlier.
	\item R-pi is also present, intersecting R-alkanes at a lower q value than
	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
	opposed to 3.7 \angstrom.
	\item R-helix and R-spots are also both missing.
	\item The line which intersected both of these features in the restrained 
	simulations faded upon equilibration which suggests that monomers in the 
	parallel-displaced configuration may not give rise to the experimental WAXS 
	pattern seen.
	\item Simulated XRD of the sandwiched configuration contains all features 
	except for R-helix.
	\item Most notably, R-spots appears in the expected location, which suggests 
	that there is something intrinsic to the sandwiched packing that gives rise 
	to such features. 
	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
	R-helix, R-pi and R-spots are not present.
  \end{itemize}

@@

  The spots that appear in the simulated XRD pattern of the sandwiched
  conformation are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains.
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (Figure~\ref{fig:tilt}). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
	\item Since the tails are mostly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:angle_distribution}).
	\item We reason that monomer tails stacked closely in the sandwiched conformation
	are forced to splay apart and pack in between in each other which creates a
	nearly hexagonal array of packed tails. 
  \end{itemize}

@@

  Basin A and Basin B are two configurationally metastable basins.
  \begin{itemize}
  	\item We hesitate to classify the basins as separate phases.
	\item We hypothesize that Basin B is present at higher temperatures.
	\item This is evidenced by a simulation of a system in Basin A whose temperature
	was linearly ramped from 280K to 340K over 100 ns.
	\item Visually, there is a distinct change in pore structure from one
	characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of 
	Basin B (Figure~\ref{fig:340K_pore}).
	\item To quantify our observation, we chose three easily measurable order 
	parameters: the distance between pores, the membrane thickness and the
	ratio of pore radius to the uncertainty in pore radius.
	\item The pore radius is divided by its uncertainty in order to understand
	the degree to which monomers obstruct the pore region.
	\item Referring back to our temperature ramped system, the slope of all 
	order parameters change around 315K - 325K 
	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
	possibility of an abrupt change in system ordering.
	\item To prove that the basins are in fact two different phases, we must 
	observe evidence of a first order phase transition, which would be marked 
	by a discontinuity in an order parameter as a function of temperature.
	\item Our 100 ns temperature ramp may have been too fast causing the system
	to suffer from hysteresis.
	%BJC: should this go in methods?
	\item To mitigate hysteresis, we performed a slow, stepwise temperature ramp.
	\item Starting from a sandwiched structure equilibrated at 280K, the system
	temperature was raised to 300K and allowed to equilibrate for 200 ns.
	\item At the end of 200 ns, the temperature was raised 5K and equilibrated 
	again for 200 ns.
	\item We continued raising the temperature by 5K and equilibrating for 200 ns
	until the system was equilibrated for 200 ns at 320K.
	\item In all cases, we observed smooth changes in order parameters as temperature
	was increased implying that we can not yet claim the existence of two phases 
	(Figure~\ref{fig:phase_transition}).
	\item I have this run out to about 335K right now. I have to see if there is anything
	noteworthy to report

@@

  The model gives reasonable estimates of ionic conductivity for both phases.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Table~\ref{table:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty.
	\item  This is especially true of the value calculated for Basin B using
	the collective diffusion model. % TODO: Run Basin B out longer
	\item Basin A collective diffusion calculations were generated from a 
	500 ns simulation.
	\item In both cases, our calculated values would benefit from longer simulations. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
	\item Conductivity is enhanced in Basin B due to a higher sodium ion diffusivity.
	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
	Sodium ions have less ites to move to in Basin A.
	\item No experimental evidence of this trend. May Xunda will find something
	\item In both cases, our calculated values for Basin A are higher than the 
	experimental values, as expected. 
	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
	\item However, the real system, although mostly aligned and straight, has a 
	distribution of azimuthal angles, meaning that the pores have a degree of 
	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
	fold increase in ionic conductivity. We would expect additional gains in a 
	perfectly aligned system.
  \end{itemize}

@@

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  Basin A.
  \begin{itemize}  %BJC: working on the following
  	\item Distribution of crosslinks
	\item Pore spacing
	\item X-ray diffraction
	\item Ionic Conductivity
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}
